### 2023-10-17 1.Introduction/motivation.tex
added more motivattion

\section{Motivation}
\label{sec:int_motivation}

Nowadays, it's impossible not to have heard about \acp{AI}, they are everywhere and everybody talks about them. The most recent example being \textit{ChatGPT} from \textbf{OpenAI} and is getting very popular even among casual computer users. Everybody is using those tools. It's clear that \ac{AI} is becoming more and more important in the current world.

\acp{AI} are very power hungry algorithms which limits its use in embedded systems and power efficient devices.
Furthermore, the time an \ac{AI} takes to compute its output quickly rises, especially on lower end chip such as the ones used in embedded systems. So much so that the most complex ones only run on online and very powerful servers, like the aforementioned \textit{ChatGPT}.

There are several options to reduce execution speed and energy consumption such as running the algorithm on a \ac{GPU} rather than on a \ac{CPU}. Using an \ac{FPGA} or \ac{ASIC} are other ways to improve power consumption and execution time.
The latter is the most restricting (as it's name implies) but has the best results.

Using an \ac{ASIC} allows the use of analog computation. Analog computation offers great advantages compared to digital computers as it's much faster while being very power-efficient.

Making an analog chip with a very low power consumption allows to use chip like that in embedded systems such as video surveillance cameras. A small chip could be installed inside the system that could be able to do gait detection \cite{gaitDS,gaitDig,gait}. The video surveillance camera would then be able to know who is showing up on the camera and if it's not a known person send an alert.

@@

Somre research \cite{celegans}, focuses on reproducing parts of the nervous system of a small organism. This could be applied on larger organisms, or, in the long term, reproduce part of the human brain. Using analog computers, small chips could be used to replace a part of one's brain non functionnal part.

The focus of this thesis is to create a working simulation of an analog \ac{LSTM} circuit using Cadence's virtuoso as simulation software. Having those preliminary results would allow for fabricating and testing such a chip. Once a working prototype is manufactured, such a circuit could highly improve embedded \ac{AI} use.

>>>>

\section{Motivation}
\label{sec:motivation}

Nowadays, it's impossible not to have heard about \acp{AI}, they are everywhere and everybody talks about them. It is common practice to advertise products using \ac{AI} powered tools. \textit{ChatGPT} from \textbf{OpenAI} is a recent example and is getting very popular even among casual computer users. Everyone is using this tool. An older example include home assistants that have been around for about ten years. Those products (such as \textbf{Amazon}'s \textit{Alexa}, \textbf{Google}'s \textit{nest} system and others) are not computing their answers locally, hence creating avoidable internet trafic. It's clear that \ac{AI} is becoming the predominant technology in the modern world and future innovations will depend on it.

\acp{AI} are very power hungry algorithms which limits its use in embedded systems and power efficient devices.
Furthermore, the time an \ac{AI} takes to compute its output quickly rises, especially on lower end chip such as the ones used in embedded systems. So much so that the most complex ones only run on online and very powerful servers, like the aforementioned \textit{ChatGPT} and home assistants.

There are several options to reduce execution speed and energy consumption such as running the algorithm on a \ac{GPU} rather than on a \ac{CPU}. Using an \ac{FPGA} or \ac{ASIC} are other ways to improve power consumption and execution time.
The latter is the most restricting, as it's name implies, but has the best results.

Using an \ac{ASIC} allows the use of analog computation. Analog computation offers great advantages compared to digital computers as it's much faster while being known to be very power-efficient.

Home assistants could greatly benefit from being able to quickly compute answers without having to connect to an online server. Locally computing answers would drastically improve the usefulness of the device. It could even allow to be used on the go, in a car for example.

Another great use for local \ac{AI} computation would be to use \acp{LLM}, the technology behind \textit{ChatGPT}, for any local use. \acp{LLM} are not the focus of the thesis, but are a long term potential objective of using analog computation for \ac{AI}.

Making an analog chip with a very low power consumption also allows to use chip like that in embedded systems such as video surveillance cameras. A small chip could be installed inside the system that could be able to do gait detection \cite{gaitDS,gaitDig,gait}. The video surveillance camera would then be able to know who is showing up on the camera and if it's not a known person send an alert.

@@

Some research \cite{celegans}, focuses on reproducing parts of the nervous system of a small organism. This could be applied on larger organisms, or, in the long term, reproduce part of the human brain. Using analog computers, small chips could be used to replace a part of one's brain non functionnal part.

The focus of this thesis is to create a working simulation of an analog \ac{LSTM} circuit using Cadence's virtuoso as simulation software. Having those preliminary results would allow to fabricate and test such a chip. Once a working prototype is manufactured, such a circuit could highly improve embedded \ac{AI} use.
